Predicting the effect of candidate interventions for mitigating disease spread in asymmetric-mixing metapopulations

### 2024-07-29 ms.tex
more refs for ethnicity intro par

\begin{itemize}
\item
  De Oliveira and colleagues tracked the spread of different SARS-CoV-2
  variants by village and by variant.
\item
  The goal of our model is two-fold. First, to identify parameters that
  could re-create the time series plots in Figure 1.
\item
  Ethnic identity is a complicated, contested concept due to coloinialism and
  various waves of oppression, repression, and genocide against Indigenous
  peoples in South America, which included various attempts at dismantling 
  and renaming pre-colonial ethnic identity~\autocite{Brandão1990}.
\item
  Second, we aim to use a parameterized model to understand how
  different intervention strategies could reduce infections among
  Reserve residents. For example, perhaps since Terena are suspected to
  travel to the
\item
  While we know a lot about transmission in the reserve, and the work of
  de Oliveira and colleagues advanced our understanding of transmission
  in the Reserve, we do not have reliable estimates of exactly how many
  cases there were per ethnicity and village. We also have only
  word-of-mouth information about the frequency of travel to the city
  for each ethnicity and location. Our model motivates the need for a
  more thorough understanding of behavior and epidemiological parameters
  in the Dourados Indigenous Reserve, and points the way towards future
  research in other Indigenous communities, and more complex situations.
  Here we only consider Indigenous mobility, but many people from the
  city travel to the reserve for commerce as well.
\end{itemize}

>>>>

\begin{itemize}
\item
  De Oliveira and colleagues tracked the spread of different SARS-CoV-2
  variants by village and by variant.
\item
  The goal of our model is two-fold. First, to identify parameters that
  could re-create the time series plots in Figure 1.
\item
  Ethnic identity is a complicated, contested concept due to coloinialism and
  various waves of oppression, repression, and genocide against Indigenous
  peoples in South America, which included various attempts at dismantling 
  and renaming pre-colonial ethnic
  identity~\autocite{Brandão1990,FerreiraThomazDeAlmeida2018,Soratto2022}.
\item
  Second, we aim to use a parameterized model to understand how
  different intervention strategies could reduce infections among
  Reserve residents. For example, perhaps since Terena are suspected to
  travel to the
\item
  While we know a lot about transmission in the reserve, and the work of
  de Oliveira and colleagues advanced our understanding of transmission
  in the Reserve, we do not have reliable estimates of exactly how many
  cases there were per ethnicity and village. We also have only
  word-of-mouth information about the frequency of travel to the city
  for each ethnicity and location. Our model motivates the need for a
  more thorough understanding of behavior and epidemiological parameters
  in the Dourados Indigenous Reserve, and points the way towards future
  research in other Indigenous communities, and more complex situations.
  Here we only consider Indigenous mobility, but many people from the
  city travel to the reserve for commerce as well.
\end{itemize}
